Modular Inverse Reinforcement Learning on Human Motion

### 2015-02-11 paper.tex
replaced avatar figure

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{avatar.png}
\caption{The task of collecting targets, avoiding obstacles and following the
path. \cite{rothkopf2013modular}}
\label{fig:avatar}
\end{figure}

Figure~\ref{fig:avatar} shows the domain that we use in this paper. The pink
cylinders represent obstacles, that the player would be punished if running
into. The blue cylinders represent targets, that the player would be rewarded if
collected. There is also a gray path on the ground that the player can follow.
So, naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles. This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.

We will evaluate four different tasks. {\bf Task 1}, following the path only, and
ignoring other objects. {\bf Task 2}, following the path, while avoid the obstacles.
{\bf Task 3}, following the path, while attain targets when possible. {\bf Task 4},
following the path, collecting the targets and avoiding obstacles
simultaneously.
We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. The human data are collected by the Center for
Perceptual Systems in University of Texas at Austin.

If the player observes the distance and angle to an object, as shown in
Figure~\ref{fig:avatar} B), he is expected to know the optimal action to avoid
or pursue it. This decision is also Markov. Therefore, the question would be, if
we have trained modules for these three subtasks, could they be integrated to
match human's behavior?

@@

We need some basic concepts in reinforcement learning to proceed. For a state, action
pair, $s$ and $a$, $Q(s, a)$ evaluates the utility of taking action $a$ from
state $s$. The {\em policy} of a state is the action with the maximum Q
value\cite{rl}. So how to we determine the global policy from the modules, or
subtasks? In the literature, work has been done to integrate the Q function
\cite{koller1999computing} or compromise on policies directly
\cite{thomas2012motor}.

>>>>

\begin{figure}[h!]
\centering
\includegraphics[height=6cm]{human.jpg}
\includegraphics[height=6cm]{env.png}
\caption{(Left) A volunteer with head tracker, virtual reality displayer, and
body tracker.  (Right) The environment the human can see through the displayer.}
\label{fig:avatar}
\end{figure}

Figure~\ref{fig:avatar} shows the domain that we use in this paper. The red
cubes represent obstacles, that the player would be punished if running
into. The blue balls represent targets, that the player would be rewarded if
collected. There is also a gray path on the ground that the player can follow.
Naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles.
This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.
We ask our volunteers to have trackers and virtual reality displayers equipped. He
can see the envrionment through the displayer in front of his eyes. So he can
walk as if he is walking in the virtual domain.

We will evaluate four different tasks. {\bf Task 1}, following the path only, and
ignoring other objects. {\bf Task 2}, following the path, while avoid the obstacles.
{\bf Task 3}, following the path, while attain targets when possible. {\bf Task 4},
following the path, collecting the targets and avoiding obstacles
simultaneously.
We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. The human data are collected by the Center for
Perceptual Systems at University of Texas at Austin.

If the player observes the distance and angle to an object, he is expected to
know the optimal action to avoid or pursue it. This decision is also Markov.
Therefore, the question would be, if we have trained modules for these three
subtasks, could they be integrated to match human's behavior?

@@

We need some basic concepts in reinforcement learning to proceed. For a state, action
pair, $s$ and $a$, $Q(s, a)$ evaluates the utility of taking action $a$ from
state $s$. The {\em policy} of a state is the action with the maximum Q
value \cite{rl}. So how to we determine the global policy from the modules, or
subtasks? In the literature, work has been done to integrate the Q function
\cite{koller1999computing} or compromise on policies directly
\cite{thomas2012motor}.
